Reading Notes

### 2020-08-25 2pd.tex
fixed error about using equations in list

%% TODO
%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps. I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process. Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
%%<IBI>
IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item {The coarse grain system is mapped onto an equilibrated atomistic one.}
    \item {The average RDF of the mapped system is calculated over the equilibrated frames of the trajectory --- this is the target distribution.}
    \item{Taking the Boltzmann Inverse (see \autoref{pmf}) of the RDF results in the potential of mean force (PMF).
        \begin{equation}
            \label{pmf}
            F(r) = -k_{B}T \ln g(r)
            \tag{\ref{pmf}}
        \end{equation}
        Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
        Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.
        }
    \item{A simulation can be run using \autoref{pmf} as the non-bonded potential to achieve a new distribution.}
    \item{The difference between the new and target distribution can be accounted for in the next iteration accoring to \autoref{ibi}.
        \begin{equation}
            \label{ibi}
            V_{i+1}(r) = V_{i}(r) - k_{B}T \ln\big(\frac{g_{i}(r)}{g(r)}\big)
            \tag{\ref{ibi}}
        \end{equation}
        Where $g_{i}(r)$ is the distribution obtained using the potential $V_{i}(r)$.
        }
\end{enumerate}
This process is repeated until the difference between the result and the target is sufficiently small.

>>>>

%% TODO
%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps. I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process. Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
%%<IBI>
IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item 
        The coarse grain system is mapped onto an equilibrated atomistic one.

    \item 
        The average RDF of the mapped system is calculated over the equilibrated frames of the trajectory --- this is the target distribution.

    \item 
        Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF):

        \[
            F(r) = -k_{B}T \ln g(r)
        \]

        Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
        Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.

    \item
        A simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.

    \item
        The difference between the new and target distribution can be accounted for in the next iteration accoring to the following equation:

        \[
            V_{i+1}(r) = V_{i}(r) - k_{B}T \ln\bigg(\frac{g_{i}(r)}{g(r)}\bigg)
        \]

        Where $g_{i}(r)$ is the distribution obtained using the potential $V_{i}(r)$.

\end{enumerate}
This process is repeated until the difference between the result and the target is sufficiently small.
